---
title: "Income Prediction Based on Race and Gender"
author: "Harshil Kurapati"
format: html
execute: 
  echo: false    
  warning: false 
  message: false 
---

```{r}
suppressPackageStartupMessages({
  library(tidyverse)
  library(primer.data)
  library(brms)
  library(tidybayes)
  library(gtsummary)
  library(ggridges)
})
```

## Introduction

This project explores the impact of race and gender on income using a Bayesian Regression Model. By examining these demographic factors, we can gain insights into how they influence income levels.

## Overview

The dataset contains demographic information such as race, gender, age, education, and income level. We will focus on race and gender as key predictors of income, applying a Bayesian Regression Model to estimate the relationship.

## Visualization

The following ridge plot shows the distribution of income by race and gender, with overlaid median income levels to provide a point of reference for comparison.

```{r}
#|cache: true
# Load libraries
library(tidyverse)
library(ggridges)
library(tidybayes)

# Load the dataset
data <- read.csv('adult.csv')

# Data preparation
data <- data %>%
  mutate(income = ifelse(income == " <=50K", "Less than 50K", "More than 50K"),
         race = factor(race, levels = c("White", "Black", "Asian-Pac-Islander", "Amer-Indian-Eskimo", "Other")),
         sex = factor(sex, levels = c("Male", "Female")))

# Dodged bar plot
ggplot(data, aes(x = race, fill = income)) + 
  geom_bar(position = position_dodge(width = 0.8), aes(y = ..prop.., group = income), width = 0.7) +
  facet_wrap(~ sex) +
  scale_y_continuous(labels = scales::percent_format()) +
  scale_fill_manual(values = c("#F8766D", "#00BFC4")) +
  labs(title = "Income Distribution by Race and Gender", 
       x = "Race",
       y = "Percentage",
       fill = "Income Level") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "top",
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank())
```


